When are Fuzzy Extractors Possible?

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
minor abstract edits

We ask: \emph{is high fuzzy min-entropy a
  sufficient condition for noise-tolerant extraction?}
If only computational security is required, recent progress on program
obfuscation gives evidence that fuzzy
min-entropy is indeed sufficient. In contrast,
information-theoretic fuzzy extractors are not known for many
practically relevant sources of high fuzzy min-entropy.

In this paper,
show that fuzzy min-entropy is also sufficient for
information-theoretically secure fuzzy extraction. For every source
distribution $W$ for which security is possible in an ideal world with
access only to the extractor functionality, we give a secure fuzzy
extractor.

Our construction relies on the extractor knowing the precise
distribution of the source $W$.  A more ambitious goal is to design a
single extractor that works for all possible sources.  We show that
this more ambitious goal is impossible: we give a family of sources
with high fuzzy min-entropy for which no single fuzzy extractor is
secure.  This result emphasizes the importance of accurate models
of high entropy sources.

>>>>

We ask: \emph{is high fuzzy min-entropy a
  sufficient condition for noise-tolerant key extraction?}
If only computational security is required, recent progress on program
obfuscation gives evidence that fuzzy
min-entropy is indeed sufficient. In contrast,
information-theoretic fuzzy extractors are not known for many
practically relevant sources of high fuzzy min-entropy.

In this paper, we show that fuzzy min-entropy is also sufficient for
information-theoretically secure fuzzy extraction. For every source
distribution $W$ for which security is possible we give a secure fuzzy
extractor.

Our construction relies on the fuzzy extractor knowing the precise
distribution of the source $W$.  A more ambitious goal is to design a
single extractor that works for all possible sources.  We show that
this more ambitious goal is impossible: we give a family of sources
with high fuzzy min-entropy for which no single fuzzy extractor is
secure.  This result emphasizes the importance of accurate models
of high entropy sources.
